\documentclass[11pt,a4paper]{article}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{url}


\author{HU, Pili}
\title{Adaptive Video Streaming: 
 \\a Survey and Case Study}

\begin{document}

\maketitle

\begin{abstract}
	In the past decade, Internet traffic has seen a significant 
	change from web browsing to video viewing. The ongoing trend 
	raises a chanllenging problem: how to stream data to heterogeous 
	peers? 
	
	The designer of such data streaming architecture should 
	bear the following considerations in mind: QoE, server load, 
	network resource efficiency, scalability, etc. The heterogeneous 
	peer network condition makes the design more complicated. The 
	underlying codec ranges from Multi Description Coding to Multi 
	Layer Coding. The data deliver architecture ranges from unicast,
	multicast, to P2P network. Researchers have focused on different 
	system settings and optimization objectives. 
	 
	This paper will first
	sum up several works in the context of adaptive video streaming. 
	At the same time, we do a case study on a commercial adaptive 
	video streaming system, which combines Multilayer Codec and P2P 
	technology. Possible improvements on this system are proposed
	with reasoning. Some of the conjectures are
	verified through a corresponding simulation platform based on NS2. 
\end{abstract}

\pagebreak
\tableofcontents
\pagebreak

\section{Introduction}



\begin{itemize}
	\item User perceived experience. 
	\item Vendor cost. 
	\item User cost. 
	\item System cost. 
\end{itemize}

\section{General Model}


\section{Problem Scope}

\subsection{Codec}

\subsection{Networking}

\section{Design of Adaptive P2P VoD System}


\subsection{Codec Choice}

\subsection{Transimission Protocol Choice}


\subsection{Overlay Construction}

\subsection{Peer Selection}


\subsection{Buffer Management}


\subsection{Chunck Selection}

MMKP, Knapsack

MCMF, Network Flow 



\subsection{Playback Decision}


\subsection{User Model}



\section{A Case Study}

\subsection{Baseline Description}

\subsection{Chunk Selection Architecture Reconstruction}


\subsection{Priority Based Upgrade}


\subsection{Scalable Window Size}


\subsection{Performance Optimization}


\subsection{Introduce Randomness in Second Window Section}


\subsection{Conclusion of the Case Study}




\section{Conclusion}

\section{Future Works}



\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}




\pagebreak
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}


\pagebreak
\addcontentsline{toc}{section}{References}
\input{gen_bib.bbl}


\end{document}